\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2019-12-09 submission/manuscript.Rmd
Added confocal images.

### Metaproteomics
Isolated proteins were whole trypsin digested using the FASP (filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK) according to the manufacturer's instructions [@Wisniewski2009] with small modifications. Before loading the solution to the column, protein pellets were solubilized in a urea sample buffer included in the kit amended with DTT (final concentration 100 \si{\milli\Molar}) for 45 \si{\minute} at room temperature and centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to remove larger particles. The first washing step after protein solution loading was repeated twice. In addition, centrifugation steps were prolonged if the column was clogged. Trypsin digestion was performed on column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}. The final filtrate containing digested proteins was acidified with 1 \si{\percent} (final concentration) trifluoroacetic acid, freezed at \num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent to the Vienna Metabolomics Center (University of Vienna) for metaproteomic analysis. **TO BE ADDED-VIENNA PART**.

@@

\newpage 
## Figure Captions

## Figures

```{r out.width="100%", fig.align="center", fig.cap="Bacteril Community\\label{community}", fig.pos="h"}
include_graphics("../results/figures/community_barplot.jpg")
```

>>>>

### Metaproteomics
Isolated proteins were whole trypsin digested using the FASP (filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK) according to the manufacturer's instructions [@Wisniewski2009] with small modifications. Before loading the solution to the column, protein pellets were solubilized in a urea sample buffer included in the kit amended with DTT (final concentration 100 \si{\milli\Molar}) for 45 \si{\minute} at room temperature and centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to remove larger particles. The first washing step after protein solution loading was repeated twice. In addition, centrifugation steps were prolonged if the column was clogged. Trypsin digestion was performed on column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}. The final filtrate containing digested proteins was acidified with 1 \si{\percent} (final concentration) trifluoroacetic acid, freezed at \num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent to the Vienna Metabolomics Center (University of Vienna) for metaproteomic analysis. Peptides were resuspended in 1 \si{\percent} (final concentration) trifluoroacetic acid, desalted using the Pierce C18 Tips (Thermo Fisher Scientific, USA) accorind to the manufacturer's instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap Mass Spectrometer (Thermo Fisher Scientific, USA). Obtaied MS/MS spectra were searched against a protein database from metagenomic assembly published in @Burke2011a using SEQUEST-HIT engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo Fisher Scientific, USA). The target-decoy approach was used to reduce the probability of false peptide identification. Results whose false discovery rate at the peptide level was \SI{< 1}{\percent} were kept. For protein identification a minimum of of two peptides and one unique peptide were required. For protein quantification, a chromatographic peak area-based free quantitative method was applied.

@@

\newpage 
\setlength\parindent{0pt}

## Figure Captions
**\autoref{micro_dec}.** \nameref{micro_dec}

**\autoref{micro_jun}.** \nameref{micro_jun}

**\autoref{community}.** \nameref{community}

\newpage
## Figures
```{r out.width="85%", fig.align="center", fig.cap="Confocal microscope images of \\textit{Cymodocea nodosa} and \\textit{Caulerpa cylindracea} surfaces from different locations (Saline, Funtana-Invaded and Funtana-Noninvaded) sampled on 4 December 2017 and stained with SYBR Green I. Scale bar in all images is 60 \\si{\\um}.\\label{micro_dec}", fig.pos="ht"}
include_graphics("../results/images/confocal_december.jpg")
```
\newpage
```{r out.width="85%", fig.align="center", fig.cap="Confocal microscope images of \\textit{Cymodocea nodosa} and \\textit{Caulerpa cylindracea} surfaces from different locations (Funtana-Invaded and Funtana-Noninvaded) sampled on 19 June 2018 and stained with SYBR Green I. Scale bar in all images is 60 \\si{\\um}.\\label{micro_jun}", fig.pos="ht"}
include_graphics("../results/images/confocal_june.jpg")
```
\newpage
```{r out.width="100%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant bacterial sequences from surfaces of two marine macrophytes (\\textit{Cymodocea nodosa} and \\textit{Caulerpa cylindracea}) sampled in different locations (Saline, Funtana-Invaded and Funtana-Noninvaded) and in two contrasting seasons (4 December 2017 and 19 June 2018).\\label{community}", fig.pos="ht"}
include_graphics("../results/figures/community_bar_plot.jpg")
```

### 2019-12-09 submission/manuscript.tex
Added confocal images.

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions (Wiśniewski \emph{et al.},
2009) with small modifications. Before loading the solution to the
column, protein pellets were solubilized in a urea sample buffer
included in the kit amended with DTT (final concentration 100
\si{\milli\Molar}) for 45 \si{\minute} at room temperature and
centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to
remove larger particles. The first washing step after protein solution
loading was repeated twice. In addition, centrifugation steps were
prolonged if the column was clogged. Trypsin digestion was performed on
column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}.
The final filtrate containing digested proteins was acidified with 1
\si{\percent} (final concentration) trifluoroacetic acid, freezed at
\num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent
to the Vienna Metabolomics Center (University of Vienna) for
metaproteomic analysis. \textbf{TO BE ADDED-VIENNA PART}.

@@

@@

@@

\begin{figure}[h]

{\centering \includegraphics[width=1\linewidth]{../results/figures/community_barplot}

@@

\caption{Bacteril Community\label{community}}\label{fig:unnamed-chunk-2}
\end{figure}

>>>>

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions (Wiśniewski \emph{et al.},
2009) with small modifications. Before loading the solution to the
column, protein pellets were solubilized in a urea sample buffer
included in the kit amended with DTT (final concentration 100
\si{\milli\Molar}) for 45 \si{\minute} at room temperature and
centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to
remove larger particles. The first washing step after protein solution
loading was repeated twice. In addition, centrifugation steps were
prolonged if the column was clogged. Trypsin digestion was performed on
column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}.
The final filtrate containing digested proteins was acidified with 1
\si{\percent} (final concentration) trifluoroacetic acid, freezed at
\num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent
to the Vienna Metabolomics Center (University of Vienna) for
metaproteomic analysis. Peptides were resuspended in 1 \si{\percent}
(final concentration) trifluoroacetic acid, desalted using the Pierce
C18 Tips (Thermo Fisher Scientific, USA) accorind to the manufacturer's
instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap
Mass Spectrometer (Thermo Fisher Scientific, USA). Obtaied MS/MS spectra
were searched against a protein database from metagenomic assembly
published in Burke \emph{et al.} (2011a) using SEQUEST-HIT engines and
validated with Percolator in Proteome Discoverer 2.1 (Thermo Fisher
Scientific, USA). The target-decoy approach was used to reduce the
probability of false peptide identification. Results \SI{< 1}{\percent}
false discovery rate at the peptide level were kept. For protein
identification a minimum of of two peptides and one unique peptide were
required. For protein quantification, a chromatographic peak area-based
free quantitative method was applied.

@@

\setlength\parindent{0pt}

@@

\textbf{\autoref{micro_dec}.} \nameref{micro_dec}

\textbf{\autoref{micro_jun}.} \nameref{micro_jun}

\textbf{\autoref{community}.} \nameref{community}

@@

\begin{figure}[ht]

{\centering \includegraphics[width=0.85\linewidth]{../results/images/confocal_december}

@@

\caption{Confocal microscope images of \textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea} surfaces from different locations (Saline, Funtana-Invaded and Funtana-Noninvaded) sampled on 4 December 2017 and stained with SYBR Green I. Scale bar in all images is 60 \si{\um}.\label{micro_dec}}\label{fig:unnamed-chunk-2}
\end{figure}\newpage

\begin{figure}[ht]

{\centering \includegraphics[width=0.85\linewidth]{../results/images/confocal_june}

\caption{Confocal microscope images of \textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea} surfaces from different locations (Funtana-Invaded and Funtana-Noninvaded) sampled on 19 June 2018 and stained with SYBR Green I. Scale bar in all images is 60 \si{\um}.\label{micro_jun}}\label{fig:unnamed-chunk-3}
\end{figure}\newpage

\begin{figure}[ht]

{\centering \includegraphics[width=1\linewidth]{../results/figures/community_bar_plot}

\caption{Taxonomic classification and relative contribution of the most abundant bacterial sequences from surfaces of two marine macrophytes (\textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea}) sampled in different locations (Saline, Funtana-Invaded and Funtana-Noninvaded) and in two contrasting seasons (4 December 2017 and 19 June 2018).\label{community}}\label{fig:unnamed-chunk-4}
\end{figure}
